Data Analysis

### 2023-04-14 ms1_data_analysis.Rmd
All results added.

library(ggplot2)
library(dplyr)
library(sjPlot)
library(AICcmodavg)

@@

We collected data on biomass (total of `r round(sum(BIOMASS$tot_bio), 0)` kg), density, and plant traits: area lost to herbivores, water content, leaf dry matter content and specific leaf area for `r length(unique(data$unified_names))` woody plant species from three tropical forest sites on elevations spanning `r 1900 - 200` m from 200 to 1900 m a.s.l. Low elevation is Wanang (200 m a.s.l.), Mid-elevation is Numba (700 m a.s.l.), and High elevation is Yawan (1900 m a.s.l.). We refer to the sites as Low, Mid- and High elevation throughout the text.

Figure 1. Median, 1st, second quadrilles, 1.5 IRQ distance, and outliers (labeled) for logarithm of biomass, richness diversity, and density for the three studied location/elevation.
```{r, echo=FALSE, results='hide', fig.show='all', warning=FALSE, message=FALSE, fig.cap= "Figure S1 Characteistics"}

@@

ggplot(elevdataT, aes(y = valueTrans, x = fsite, label = garden))+
  geom_boxplot()+
  geom_text(aes(label=outlier), hjust = 1.2, vjust = -0.0005, na.rm=TRUE)+
  facet_grid(vars(descriptor), vars(treatment), scales = "free")+
  theme_bw()

@@

Looking at the control plots Numba (the mid-elevation in our study) has the highest abundance and number of species. Predictably productivity decreases with elevation. Control plots in Numba are more variable than in other two elevations. Yawan has one site with lowest abundance (garden number seven).However no significant differences in variance were detected (Levene's and Bartellet's tests)

@@

# Stack the data and rename descriptor names
for (file in names(dats)){
  print(file)
  dat <- dats[[file]]
  dat$descriptor <- ifelse(grepl("bio", file), "Biomass",
                           ifelse(grepl("dens", file), "Woody plant density",
                                  ifelse(grepl("div", file),"Diversity", "Richness")))
  dat <- dat[, c("site", "garden", "treatment", "lratio","descriptor")]
  panel_data <- rbind(dat, panel_data)
}

@@

# library(dplyr)
# library(ggplot2)
# library(GGally)
# library(lme4)
# library(lmerTest)
# library(ggpmisc)
# library(tibble)

# LRR correlation plot

ftreats <- unique(panel_data$ftreatment)

@@

      print(paste(resp, desc,loc))

@@

      print(paste(desc,loc))

@@

      # Test for normality
      print(shapiro.test(lrrtd$x))
      print(shapiro.test(lrrtd$y))

@@

      print(lm.test.p)

@@

### COMMUNITY COMPOSITION

@@

  print(site.id)

@@

  print(anova(rdamod, permutations = h, by = "terms"))

@@

# library(betapart)
# 
# csites <- grepl("_c\\b", COMMVARS$plotid)
# fsites <- grepl("_f", COMMVARS$plotid)
# isites <- grepl("_i", COMMVARS$plotid)
# hsites <- grepl("_h", COMMVARS$plotid)
# psites <- grepl("_p", COMMVARS$plotid)
# 
# wsites <- COMMVARS$site == "wanang"
# nsites <- COMMVARS$site == "numba"
# ysites <- COMMVARS$site == "yawan"
# 
# # B-C dissimilarities in C plots between sites
# cdatc <- COMMDATA[grepl("c$", rownames(COMMDATA)), ]
# cvars <- COMMVARS[rownames(cdatc), ]
# 
# # Make a matrix
# for(i in 1:dim(cdatc)[1]){
#   
#   # Compare all other sites to the current i
#   for (j in (1:dim(cdatc)[1])[-i]) {
#     val <- beta.pair.abund(cdatc[c(i,j), ])
#   }
#   
# }
# 
# # Comparisons between
# wc.beta <- beta.pair.abund(COMMDATA[COMMVARS[wsites & csites,]$plotid,  ])
# 
# beta.df <- data.frame()
# 
# for(siteid in c("w","y","n")){
#   for(treat in c("_c\\b","_f","_h","_i","_p")){
#     
#     # Subset the data
#     nms <- rownames(COMMDATA)
#     sel.nms <- nms[grepl(siteid, nms) & grepl(treat, nms)]
#     site.treat.comm <- COMMDATA[sel.nms,]
#     
#     print(rownames(site.treat.comm))
#     
#     # Calculate beta diversity
#     subbeta <- beta.pair.abund(site.treat.comm)
#     
#     # Add to a data frame
#     balanced.df <- data.frame(site = siteid,
#                               treat = treat,
#                               vals = as.numeric(subbeta$beta.bray.bal),
#                               component = "balanced")
#     
#     gradient.df <- data.frame(site = siteid,
#                               treat = treat,
#                               vals = as.numeric(subbeta$beta.bray.gra),
#                               component = "gradient")
#     
#     bray.df <- data.frame(site = siteid,
#                               treat = treat,
#                               vals = as.numeric(subbeta$beta.bray),
#                               component = "bray")
#     
#     sub.df <- rbind(balanced.df, gradient.df, bray.df)
#       
#     # Merge the datset
#     beta.df <- rbind(beta.df,sub.df)
#     
#   }
# }

@@

# 
# # Fix the site order
# beta.df$fsite <- factor(beta.df$site, levels = c("w","n","y"))
# 
# # Transform 0s to 0.001 and 1s to 0.999
# beta.df$trans.vals = ifelse(beta.df$vals == 1, 0.999999, 
#                             ifelse(beta.df$vals == 0, 0.000001, beta.df$vals))
# 
# # Tests for individual facets
# 
# library(lsmeans)
# library(emmeans)
# library(multcomp)
# library(multcompView)
# 
# cld.dat = data.frame()
# prws.comp <- list()
# 
# # CLD data for comparisons between elevations
# for (comp in unique(beta.df$component)){
#   print(comp)
#   for (trt in unique(beta.df$treat)){
#     print(trt)
#     
#     test.df <- beta.df %>%
#       filter(treat == trt,
#              component == comp)
#     
#     # print(test.df)
#     
#     mod1 <- betareg::betareg(trans.vals ~ fsite, data = test.df)
#     
#     lsmod1 <- lsmeans(mod1,
#                       pairwise ~ fsite,
#                       adjust="tukey")
#     
#     groups <- cld(lsmod1, Letters = c("abcdefg"))
#     
#     y_loc = test.df %>%
#       group_by(fsite) %>%
#       summarise(y_loc = mean(trans.vals))
#     
#     sub.cld <- data.frame(component = comp,
#                treat = trt,
#                fsite = groups$fsite,
#                gr.label = groups$.group,
#                y_loc = y_loc$y_loc[order(groups$fsite)])
#     
#     print(y_loc)
#     print(sub.cld)
#     
#     prws.comp[[paste(comp,trt)]] <- lsmod1
#     
#     cld.dat = rbind(cld.dat, sub.cld)
#     
#   }
# }
# 
# # cld.dat = data.frame()
# # prws.comp <- list()
# 
# # For data for comparisons between treatments we need pairwise comps 
# # (control vs treat) - this can be obtained from summary of the betareg
# 
# # library(glmmTMB)
# 
# pairwise.comp.res <- data.frame()
# for (comp in unique(beta.df$component)){
#   
#   for (ste in unique(beta.df$fsite)){
#     print(comp)
#     print(ste)
#     
#     test.df <- beta.df %>%
#       filter(fsite == ste,
#              component == comp)
#     
#     # print(test.df)
#     
#     mod1 <- betareg::betareg(trans.vals ~ treat, data = test.df)
#     
#     breg.table <- summary(mod1)$coefficients$mean
#     breg.pvals <- breg.table[,4]
#     
#     y_loc = test.df %>%
#       group_by(treat) %>%
#       summarise(y_loc = mean(trans.vals))
#     
#     pcr.row <- data.frame(comp = comp,
#                           fsite = ste,
#                           component = comp,
#                           treat = names(breg.pvals),
#                           p.vals = breg.pvals,
#                           y_loc = y_loc$y_loc,
#                           y_loc_trt = y_loc$treat)
#     
#     pcr.row <- pcr.row %>%
#       mutate(label = ifelse(p.vals <= 0.05 & treat != "(Intercept)", "*",""))
#     
#     pairwise.comp.res <- rbind(pairwise.comp.res,pcr.row)
#     
#   }
# }
# 
# pairwise.comp.res
# 
# # Plot
# # tiff(filename='figures/beta_part_panel.tif',
# #      height=5600,
# #      width=5600,
# #      units='px',
# #      res=800,compression='lzw')
# beta.part.plot <- ggplot(beta.df, aes(x = fsite, y = vals))+
#   geom_jitter(width = 0.1, alpha = 0.2, shape = 16, size = 1.8)+
#   stat_summary(fun.y = mean, na.rm = T,
#                geom = "point", size = 3, col = "gray30")+
#   stat_summary(fun.data = "mean_cl_boot", col = "gray30")+
#   stat_summary(fun.y = mean, aes(group = treat),
#                geom = "line", alpha = 0.8, col = "gray30", lty = 2)+
#   geom_text(data = cld.dat,
#             aes(x = fsite, y = y_loc + 0.5,
#                 label = gr.label),
#             size = 3)+
#   facet_grid(cols = vars(component), rows = vars(treat))
# beta.part.plot + theme_bw()
# 
# # Plot for the component comparisons
# pairwise.comp.res$fsite <- factor(pairwise.comp.res$fsite, levels = c("w","n","y"))
# 
# # tiff(filename='figures/beta_part_panel_treats.tif',
# #      height=5600,
# #      width=5600,
# #      units='px',
# #      res=800,compression='lzw')
# 
# # Alternative boxplot
# beta.part.plot <- ggplot(beta.df, aes(x = treat, y = vals))+
#   geom_boxplot()+
#   # stat_summary(fun.y = mean, na.rm = T,
#   #              geom = "point", size = 3, col = "gray30")+
#   # stat_summary(fun.data = "mean_cl_boot", col = "gray30")+
#   geom_text(data = pairwise.comp.res,
#             aes(x = y_loc_trt, y = y_loc + 0.5,
#                 label = label), cex = 6,  col = "red", lwd = 2)+
#   facet_grid(component ~ fsite)
# 
# beta.part.plot + theme_bw()

@@

### Trait based analyses

@@

# ENCLOSED IN THE get_ready_for_the_sla_analyses
# Subset a data-set to only control and treatment plots 
subDat <- dwbRichF %>%
  filter(treatment %in% subsetVars)

lgsData <- data.frame()

for (st in unique(subDat$site)){
  for (gard in unique(subDat$garden)){

    stGardDat <- subDat %>%
            filter(site == st,
                   garden == gard)

    # Some quality control
    if(dim(stGardDat)[1] == 0){
      next
      }
    if(length(unique(stGardDat$treatment)) < 2){
      next
      }

    specInCtr <- unique(stGardDat[stGardDat$treatment == subsetVars[1], ]$unified_names)
    specInTrt <- unique(stGardDat[stGardDat$treatment == subsetVars[2], ]$unified_names)

    spLost <- specInCtr[!(specInCtr %in% specInTrt)]
    spGained <- specInTrt[!(specInTrt %in% specInCtr)]

    stGardDat$pg.cat <- ifelse(stGardDat$unified_names %in% spLost, "lost",
                               ifelse(stGardDat$unified_names %in% spGained, "gained", "stayed"))

    lgsData <- rbind(lgsData, stGardDat)

  }
}
```

@@

# Function that performs RF analysis for a given treatment

# It queries the lgsData that needs to be preapred using separate code (as above)

getLgsData <- function (comp.trt = "i", data) {

  # This function queries the data to compute log

# Returns:
# 1) Classifier RF table
# 2) Confusion matrix
# 3) Regression tree example graph

runRF <- function (lgsData) {

```{r}
# Random Forest
# Loading package
library(caTools)
library(randomForest)

rfData <- lgsData %>%
  mutate(pg.cat = as.factor(pg.cat),
         lest.leaf.area = log(est.leaf.area),
         lstem = log(no_stems)) %>%
  dplyr::select(pg.cat, lstem, perc.herb, water.cont,
                lest.leaf.area, richness, ltb, lsla.d, treatment)

# Try standardized, non-correlated variables
rfDataRF <- rfData %>%
  filter(!is.infinite(lest.leaf.area)) %>%
  dplyr::select(pg.cat, perc.herb, water.cont,
                richness, ltb, lsla.d)

# Standardized
rfDataRF[,-1] <- scale(rfDataRF[,-1])

@@

@@

@@

Below is a confusion matrix for the RF

```{r, results='asis'}
# Confusion Matrix
confusion_mtx = table(test[, 1], y_pred)
print(knitr::kable(confusion_mtx))
```

@@

library(rpart)
library(rpart.plot)

# Regression C50
library(C50)
library(printr)

C50Fit <- C5.0(pg.cat ~., data=train,
               control = C5.0Control(minCases = 5))

C50pred <- predict(object=C50Fit, 
                   newdata=test, 
                   type="class")

plot(C50Fit, cex = 0.5)

Lets see how good of a job the regression tree did.

print(knitr::kable(table(C50pred, test$pg.cat)))

@@

@@

```
```{r}
# Test for the relationship and the differences
require(sjPlot)
cwm.lm <- lm(log(cwm.sla)~log(sp.rich)*treatment + site, data = siteSLAdf)
cwm.lm.nosite <- lm(log(cwm.sla)~log(sp.rich)*treatment, data = siteSLAdf)
cwm.lm.nosite.noint <- lm(log(cwm.sla)~log(sp.rich)+treatment, data = siteSLAdf)
cwm.lm.onlysp <- lm(log(cwm.sla)~log(sp.rich), data = siteSLAdf)

>>>>

library(ggplot2)
library(dplyr)
library(sjPlot)
library(AICcmodavg)
library(caTools)
library(randomForest)
library(rpart)
library(rpart.plot)
library(C50)
library(printr)
library(betapart)
library(lsmeans)
library(emmeans)
library(multcomp)
library(multcompView)

@@

We collected data on biomass (total of `r round(sum(BIOMASS$tot_bio), 0)` kg), density, and plant traits: area lost to herbivores, water content, leaf dry matter content and specific leaf area for `r length(unique(data$unified_names))` woody plant species from three tropical forest sites: low elevation (Wanang, 200 m a.s.l.); mid-elevation (Numba, 700 m a.s.l.); high elevation (Yawan, 1900 m a.s.l.). We refer to the sites as Low, Mid- and High elevation throughout the text.

@@

# Tests and labels

labelsS1 <- data.frame()

for (desc in unique(elevdataT$descriptor)){
  for (trt in unique(elevdataT$treatment)){
    subdat <- elevdataT %>% filter(descriptor == desc & treatment == trt)
    subdat %>% 
      group_by(fsite) %>%
      summarize(ycoord = mean(valueTrans)) %>%
      dplyr::select(ycoord)
    mod1 <- lm(valueTrans ~ fsite, data = subdat)
    anova(mod1)
    lbls <- cld(object = emmeans(mod1, specs = "fsite"),Letters = c("a","b","c"))$.group

    print(paste(desc, trt, paste0(lbls, collapse = "")))

    labelsS1 <- rbind(labelsS1, data.frame(descriptor = desc,
                                           sites = factor(c("wanang", "numba", "yawan"),
                                                          levels = c("wanang", "numba", "yawan")),
                                           labels = lbls,
                                           treatment = trt,
                                           ycoord = subdat %>% 
                                             group_by(fsite) %>%
                                             summarize(ycoord = mean(valueTrans)) %>%
                                             dplyr::select(ycoord)))
  }
}

@@

```{r, echo=FALSE, results='hide', fig.show='all', warning=FALSE, message=FALSE, fig.cap=" Figure S1. Median, 1st, 2nd quadrilles, 1.5 IRQ distance, and outliers (labeled) for logarithm of biomass, richness diversity, and density at three studied locations/elevations. Letters indicate statisitcal differences at the $\alpha$ = 0.05 level from the post hos Tukey test."}
# Plot
ggplot(elevdataT, aes(y = valueTrans, x = fsite, label = garden))+
  geom_boxplot()+
  geom_text(aes(label=outlier), 
            size = 2, 
            alpha = 0.6,
            hjust = 1.2, 
            vjust = -0.0005, 
            na.rm=TRUE) +
  facet_grid(vars(descriptor), vars(treatment), scales = "free")+
  geom_text(data = labelsS1,
            aes(x = sites, y = ycoord + 2.5, group = trt,
                label = labels),
            size = 3) +
  theme_bw() +
  theme(strip.text = element_text(size =5.5),
        axis.text.x = element_text(angle = 45,
                                   hjust = 1))+
  xlab("")

Elevations were similar in their baseline productivity (total biomass). Mid and high elevations had the highest baseline productivity (total biomass). Abundance and species richness.  decreased with elevation. Control plots in Numba are more variable than in other two elevations. Yawan has one site with lowest abundance (garden number seven).However no significant differences in variance were detected (Levene's and Bartellet's tests)

@@

# Stack the data and rename descriptor names
for (file in names(dats)){
  # print(file)
  dat <- dats[[file]]
  dat$descriptor <- ifelse(grepl("bio", file), "Biomass",
                           ifelse(grepl("dens", file), "Woody plant density",
                                  ifelse(grepl("div", file),"Diversity", "Richness")))
  dat <- dat[, c("site", "garden", "treatment", "lratio","descriptor")]
  panel_data <- rbind(dat, panel_data)
}

@@

# LRR correlation plot
ftreats <- unique(panel_data$ftreatment)

@@

      # print(paste(resp, desc,loc))

@@

      # print(paste(desc,loc))

@@

@@

@@

## COMMUNITY COMPOSITION

@@

  # print(site.id)

@@

  # print(anova(rdamod, permutations = h, by = "terms"))

@@

csites <- grepl("_c\\b", COMMVARS$plotid)
fsites <- grepl("_f", COMMVARS$plotid)
isites <- grepl("_i", COMMVARS$plotid)
hsites <- grepl("_h", COMMVARS$plotid)
psites <- grepl("_p", COMMVARS$plotid)

wsites <- COMMVARS$site == "wanang"
nsites <- COMMVARS$site == "numba"
ysites <- COMMVARS$site == "yawan"

# B-C dissimilarities in C plots between sites

cdatc <- COMMDATA[grepl("c$", rownames(COMMDATA)), ]
cvars <- COMMVARS[rownames(cdatc), ]

# Make a matrix
# for(i in 1:dim(cdatc)[1]){
#   # Compare all other sites to the current i
#   for (j in (1:dim(cdatc)[1])[-i]) {
#     val <- beta.pair.abund(cdatc[c(i,j), ])
#   }
# }

# Comparisons between
wc.beta <- beta.pair.abund(COMMDATA[COMMVARS[wsites & csites,]$plotid,  ])

beta.df <- data.frame()

for(siteid in c("w","y","n")){
  for(treat in c("_c\\b","_f","_h","_i","_p")){

    # Subset the data
    nms <- rownames(COMMDATA)
    sel.nms <- nms[grepl(siteid, nms) & grepl(treat, nms)]
    site.treat.comm <- COMMDATA[sel.nms,]

    print(rownames(site.treat.comm))

    # Calculate beta diversity
    subbeta <- beta.pair.abund(site.treat.comm)

    # Add to a data frame
    balanced.df <- data.frame(site = siteid,
                              treat = treat,
                              vals = as.numeric(subbeta$beta.bray.bal),
                              component = "balanced")

    gradient.df <- data.frame(site = siteid,
                              treat = treat,
                              vals = as.numeric(subbeta$beta.bray.gra),
                              component = "gradient")

    bray.df <- data.frame(site = siteid,
                              treat = treat,
                              vals = as.numeric(subbeta$beta.bray),
                              component = "bray")

    sub.df <- rbind(balanced.df, gradient.df, bray.df)

    # Merge the datset
    beta.df <- rbind(beta.df,sub.df)

@@

# Fix the site order
beta.df$fsite <- factor(beta.df$site, levels = c("w","n","y"))

# Transform 0s to 0.001 and 1s to 0.999
beta.df$trans.vals = ifelse(beta.df$vals == 1, 0.999999,
                            ifelse(beta.df$vals == 0, 0.000001, beta.df$vals))

# Tests for individual facets
cld.dat = data.frame()
prws.comp <- list()

# CLD data for comparisons between elevations
for (comp in unique(beta.df$component)){
  print(comp)
  for (trt in unique(beta.df$treat)){
    print(trt)

    test.df <- beta.df %>%
      filter(treat == trt,
             component == comp)

    # print(test.df)

    mod1 <- betareg::betareg(trans.vals ~ fsite, data = test.df)

    lsmod1 <- lsmeans(mod1,
                      pairwise ~ fsite,
                      adjust="tukey")

    groups <- cld(lsmod1, Letters = c("abcdefg"))

    y_loc = test.df %>%
      group_by(fsite) %>%
      summarise(y_loc = mean(trans.vals))

    sub.cld <- data.frame(component = comp,
               treat = trt,
               fsite = groups$fsite,
               gr.label = groups$.group,
               y_loc = y_loc$y_loc[order(groups$fsite)])

    print(y_loc)
    print(sub.cld)

    prws.comp[[paste(comp,trt)]] <- lsmod1

    cld.dat = rbind(cld.dat, sub.cld)

# cld.dat = data.frame()
# prws.comp <- list()
# 
# # For data for comparisons between treatments we need pairwise comps 
# # (control vs treat) - this can be obtained from summary of the betareg
# 
# # library(glmmTMB)

pairwise.comp.res <- data.frame()
for (comp in unique(beta.df$component)){

  for (ste in unique(beta.df$fsite)){
    print(comp)
    print(ste)

    test.df <- beta.df %>%
      filter(fsite == ste,
             component == comp)

    # print(test.df)

    mod1 <- betareg::betareg(trans.vals ~ treat, data = test.df)

    breg.table <- summary(mod1)$coefficients$mean
    breg.pvals <- breg.table[,4]

    y_loc = test.df %>%
      group_by(treat) %>%
      summarise(y_loc = mean(trans.vals))

    pcr.row <- data.frame(comp = comp,
                          fsite = ste,
                          component = comp,
                          treat = names(breg.pvals),
                          p.vals = breg.pvals,
                          y_loc = y_loc$y_loc,
                          y_loc_trt = y_loc$treat)

    pcr.row <- pcr.row %>%
      mutate(label = ifelse(p.vals <= 0.05 & treat != "(Intercept)", "*",""))

    pairwise.comp.res <- rbind(pairwise.comp.res,pcr.row)

pairwise.comp.res

# # Plot
# # tiff(filename='figures/beta_part_panel.tif',
# #      height=5600,
# #      width=5600,
# #      units='px',
# #      res=800,compression='lzw')

beta.part.plot1 <- ggplot(beta.df, aes(x = fsite, y = vals))+
  geom_jitter(width = 0.1, alpha = 0.2, shape = 16, size = 1.8)+
  stat_summary(fun.y = mean, na.rm = T,
               geom = "point", size = 3, col = "gray30")+
  stat_summary(fun.data = "mean_cl_boot", col = "gray30")+
  stat_summary(fun.y = mean, aes(group = treat),
               geom = "line", alpha = 0.8, col = "gray30", lty = 2)+
  geom_text(data = cld.dat,
            aes(x = fsite, y = y_loc + 0.5,
                label = gr.label),
            size = 3)+
  facet_grid(cols = vars(component), rows = vars(treat)) + 
  theme_bw()

# Plot for the component comparisons
pairwise.comp.res$fsite <- factor(pairwise.comp.res$fsite, levels = c("w","n","y"))

# # tiff(filename='figures/beta_part_panel_treats.tif',
# #      height=5600,
# #      width=5600,
# #      units='px',
# #      res=800,compression='lzw')

# Alternative boxplot
beta.part.plot2 <- ggplot(beta.df, aes(x = treat, y = vals))+
  geom_boxplot()+
  # stat_summary(fun.y = mean, na.rm = T,
  #              geom = "point", size = 3, col = "gray30")+
  # stat_summary(fun.data = "mean_cl_boot", col = "gray30")+
  geom_text(data = pairwise.comp.res,
            aes(x = y_loc_trt, y = y_loc + 0.5,
                label = label), cex = 6,  col = "red", lwd = 2)+
  facet_grid(component ~ fsite) + 
  theme_bw()
```

```{r, fig.width=10, fig.height=18}
ggpubr::ggarrange(beta.part.plot1,
                  beta.part.plot2, nrow = 2)
```

@@

### Traits and species faith

@@

# ENCLOSED IN THE get_ready_for_the_sla_analyses
# Subset a data-set to only control and treatment plots 
# subDat <- dwbRichF %>%
#   filter(treatment %in% subsetVars)
# 
# lgsData <- data.frame()
# 
# for (st in unique(subDat$site)){
#   for (gard in unique(subDat$garden)){
#     
#     stGardDat <- subDat %>%
#             filter(site == st,
#                    garden == gard)
#     
#     # Some quality control
#     if(dim(stGardDat)[1] == 0){
#       next
#       }
#     if(length(unique(stGardDat$treatment)) < 2){
#       next
#       }
#     
#     specInCtr <- unique(stGardDat[stGardDat$treatment == subsetVars[1], ]$unified_names)
#     specInTrt <- unique(stGardDat[stGardDat$treatment == subsetVars[2], ]$unified_names)
#     
#     spLost <- specInCtr[!(specInCtr %in% specInTrt)]
#     spGained <- specInTrt[!(specInTrt %in% specInCtr)]
#     
#     stGardDat$pg.cat <- ifelse(stGardDat$unified_names %in% spLost, "lost",
#                                ifelse(stGardDat$unified_names %in% spGained, "gained", "stayed"))
#     
#     
#     lgsData <- rbind(lgsData, stGardDat)
#     
#     
#   }
# }
```

@@

```{r, results='asis'}
# Random Forest
# Loading package

rfAnalysis <- function(lgsData) {

  rfData <- lgsData %>%
  mutate(pg.cat = as.factor(pg.cat),
         lest.leaf.area = log(est.leaf.area),
         lstem = log(no_stems)) %>%
  dplyr::select(pg.cat, lstem, perc.herb, water.cont,
                lest.leaf.area, richness, ltb, lsla.d, treatment)
  # Try standardized, non-correlated variables
  rfDataRF <- rfData %>%
    filter(!is.infinite(lest.leaf.area)) %>%  
    dplyr::select(pg.cat, perc.herb, water.cont, richness, ltb, lsla.d)
  # Standardized
  rfDataRF[,-1] <- scale(rfDataRF[,-1])

@@

  # Confusion Matrix
  confusion_mtx = table(test[, 1], y_pred)

  # Regression C50
  C50Fit <- C5.0(pg.cat ~., data=train,
                 control = C5.0Control(minCases = 5))
  C50pred <- predict(object=C50Fit, 
                     newdata=test, 
                     type="class")

  # return(list(rf_confusion_matrix = confusion_mtx,
  #             classifier_for_varImpPlot = varImpPlot(classifier_RF),
  #             reg_tree_table = table(C50pred, test$pg.cat),
  #             reg_fit_for_plot = plot(C50Fit, cex = 0.5)))

  return(list(rf_confusion_matrix = confusion_mtx,
              classifier_for_varImpPlot = classifier_RF,
              reg_tree_table = table(C50pred, test$pg.cat),
              reg_fit_for_plot = C50Fit))

# rfData <- lgsData %>%
#   mutate(pg.cat = as.factor(pg.cat),
#          lest.leaf.area = log(est.leaf.area),
#          lstem = log(no_stems)) %>%
#   dplyr::select(pg.cat, lstem, perc.herb, water.cont,
#                 lest.leaf.area, richness, ltb, lsla.d, treatment)
# 
# # Try standardized, non-correlated variables
# rfDataRF <- rfData %>%
#   filter(!is.infinite(lest.leaf.area)) %>%
#   dplyr::select(pg.cat, perc.herb, water.cont,
#                 richness, ltb, lsla.d)
# 
# # Standardized
# rfDataRF[,-1] <- scale(rfDataRF[,-1])
# 
# # Splitting data in train and test data
# split <- sample.split(rfDataRF, SplitRatio = 0.7)
# train <- subset(rfDataRF, split == "TRUE")
# test <- subset(rfDataRF, split == "FALSE")
#   
# classifier_RF = randomForest(x = train[-1],
#                              y = train$pg.cat,
#                              ntree = 500)

@@

# Predicting the Test set results
# y_pred = predict(classifier_RF, newdata = test[-1])

@@

@@

# Run all random forests

subsetVars <- c("c", "p")
source('code/get_data_ready_for_the_sla_analyses.R')
prfres <- rfAnalysis(lgsData)

subsetVars <- c("c", "i")
source('code/get_data_ready_for_the_sla_analyses.R')
irfres <- rfAnalysis(lgsData)

subsetVars <- c("c", "f")
source('code/get_data_ready_for_the_sla_analyses.R')
frfres <- rfAnalysis(lgsData)

subsetVars <- c("c", "h")
source('code/get_data_ready_for_the_sla_analyses.R')
hrfres <- rfAnalysis(lgsData)

@@

```{r, figures-side, fig.show="hold", out.width="50%"}
varImpPlot(prfres$classifier_for_varImpPlot,
           main = 'Variable Importance for the predator exclusion')
varImpPlot(irfres$classifier_for_varImpPlot,
           main = 'Variable Importance for the insect exclusion')
varImpPlot(frfres$classifier_for_varImpPlot,
           main = 'Variable Importance for the fungi exclusion')
varImpPlot(hrfres$classifier_for_varImpPlot,
           main = 'Variable Importance for the herbivore addition')
```

@@

```
```{r, results='asis'}
# Test for the relationship and the differences
require(sjPlot)
cwm.lm <- lm(log(cwm.sla)~log(sp.rich)*treatment + site, data = siteSLAdf)
cwm.lm.nosite <- lm(log(cwm.sla)~log(sp.rich)*treatment, data = siteSLAdf)
cwm.lm.nosite.noint <- lm(log(cwm.sla)~log(sp.rich)+treatment, data = siteSLAdf)
cwm.lm.onlysp <- lm(log(cwm.sla)~log(sp.rich), data = siteSLAdf)
